A Tale of Two Transects

### 2019-03-18 writing/transect_paper.Rmd
Start of methods outline

>>>>

## Sampling

## Soil Chemistry

## DNA extraction, PCR, and sequencing

  - lysis in field Zymo Research Xpedition kit
  - short amplicon : gITS7 -- ITS4 (multiplexing index on gITS7)
  - long amplicon : ITS1 -- LR5 (multiplexing index on both ends)
  - short amplicon : same library sequenced with PacBio RS II and Ion Proton S5
  - long amplicon : PacBio RS II

## Bioinformatics

  - Two workflows for short reads:
    - Mohammad's workflow in Pipecraft
    - Brendan's workflow using Snakemake/Drake

  - Brendan's pipeline:
      - Ion Torrent
          - used demultiplexing from SciLife (standard IonXpress)
          - primers removed with `cutadapt` [@martin2011]
      - PacBio
          - CCS basecalls re-done with `ccs` version ___ [@pacificbiosciences2019]
          - demultiplexed and primers removed with `cutadapt` [@martin2011]
      - ITS1, ITS2, ITS, LSU extracted using ITSx [@Nilsson2010, @bengtsson-palme2013]
      - extracted regions independently quality filtered by max expected error using `dada2::filterAndTrim()`
      - dereplicated using `dada2::derepFastq()`
      - denoised with `dada2::dada()`
      - de novo chimera removal using `dada2::removeBimeraDenovo()`
      - taxonomy assigned using `dada2::assignTaxonomy()` with Unite database (ITS, ITS1, ITS2, long, short)[@nilsson2019a], RDP (LSU, long)[@cole2014], and Silva (LSU, long) databases
## Statistics
